Experiment_2_modelling

### 2020-01-27 Experiment_2/Experiment_2_modelling.Rmd
added naive tom and qls with transfer

```{r}
# Assumes within game transfer of opponent model between stages, but boolena for between game transfer. 
TOM_model <- function(par, data, opp_strategy_vec, return_value, within_transfer, btwn_transfer) {

@@

      ## KEY CODE FOR LEARNING TRANSFER !! (if no OM transfer reset prior to uniform)#####
      # Round 1 of stage 1 
      if (data[t,"stage"] == 1) {
        if (btwn_transfer){
          # if there is between game transfer, then the opp_prior_vec should have stored what was learned about the SECOND opponent 
          # ...from stage 4 of previous game (or uniform if it is first game of RPS). store that before proceeding
          opp2_prior_vec <- opp_prior_vec
          # if between game transfer use stored opp1 prior vector from previous game (or uniform if first game  RPS) 
          opp_prior_vec <- opp1_prior_vec

        } else { # <- No between game TRANSFER 
          opp_prior_vec <- rep(1/num_strat, num_strat)
        }

@@

@@

TOM_model(c(0.5,0.1),test_data,c("level0","level1","level2"),"-2loglik", within_transfer = TRUE, btwn_transfer = TRUE)
```
## Fitting Bayesian model with between game transfer (as well as within)  
```{r, cache=TRUE}
exp2_BT <- list()
for(id in unique(dat_exp2$human_id)) {
  exp2_BT[[id]] <- list()
  tdat <- subset(dat_exp2,human_id == id)

@@

  exp2_BT[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = TRUE, btwn_transfer = TRUE,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
}
save(exp2_BT, file="exp2_BT.RData")

@@

  exp2_NO_BT[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = TRUE, btwn_transfer = FALSE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
}

@@

  exp2_NO_Tr[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = FALSE , btwn_transfer = FALSE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
}

@@

## Fitting Q_learning with state space of possible last round plays 
```{r, cache=TRUE}
exp2_QL_states <- function(par,data,return_value,gamma){
  # Par[1] -> beta= inverse temperature parameter in softmax choice function
  # Par[2] -> lambda = learning rate (one per game?)
  # data : participant and ai choice data.
  # return_value=c("-2loglik","likelihood_by_trial")
  # Gamma is discount factor for future rewards 
  # Returns Q-values per trial and predicts choice using softmax
  beta <- par[1]
  alpha <- par[2]

@@

    if(data[t,"round"] == 1) {
      # first round is uniform prediction
      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, shootout = Q_vals_SHOOT)
      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, shootout = states_SHOOT)
      lik_hum[t] <- 1/nopts
      # Randomly select state and previous actions for first round
      curr_state <- sample(state_vec, size = 1)
      h_act <- sample(colnames(Q_vals), size =1)
      ai_act <- sample(colnames(Q_vals), size =1)
      reward <- 0

@@

    # Assume human chooses action probabilistically using softmax on Q values
    probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
    #if (data[t,"round"] == 20) { cat(probs,"\n") }

@@

```{r}
exp2_QL_states(c(5,0.4),test_data, "-2loglik", 0.0)
```

@@

@@

# Load various modelling tables 
# 
# load("exp2_BT.RData")
# load("exp2_NO_BT.RData")
# load("exp2_NO_Tr.RData")
# load("exp2_QLS_modelling.RData")
# load("exp2_SEWA_modelling.RData")
# load("MBM2_modelling.RData")

@@

                         # Bayesian updating with/without transfer
                         "Btwn_TR_BIC" = exp2_BT[[id]]$value + 2*log(180),
                         "No_Btwn_Tr_BIC" = exp2_NO_BT[[id]]$value+ 2*log(180),
                         "No_Tr_BIC" = exp2_NO_Tr[[id]]$value+ 2*log(180),

                         # Theta is the parameter governing AI stochasticity. Truth is 0.9
                         "theta_transfer" = exp2_BT[[id]]$par[1],
                         "theta_no_btw_tr" = exp2_NO_BT[[id]]$par[1],
                         "theta_no_tr" =  exp2_NO_Tr[[id]]$par[1],
                         # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
                         "eps_transfer" = exp2_BT[[id]]$par[2],
                         "eps_no_btwn_tr" = exp2_NO_BT[[id]]$par[2],
                         "eps_no_tr" = exp2_NO_Tr[[id]]$par[2],

                         # Q-learning with last round states
                         "QL_states_BIC" = exp2_QLS_modelling[[id]]$optim$bestval + 2*log(180),
                         # beta ->  inverse temperature parameter in softmax choice function
                         "QL_states_Beta" = exp2_QLS_modelling[[id]]$optim$bestmem[1],
                         # alpha -> learning rate in QL update
                         "QL_states_alpha" = exp2_QLS_modelling[[id]]$optim$bestmem[2],

@@

```{r}
exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT", "QL_states","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])

@@

```{r}
exp2_model_comp <- data.frame()
for(id in unique(dat_exp2$human_id)) {
  tdat <- subset(dat_exp2,human_id == id)
  tot_score <- sum(tdat$score)
  tot_time <- sum(tdat$human_rt)
  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg"))
  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
  tr_score <- sum(early_dat$score)
  id_results <- subset(exp2_results, ID == id)
  min_BIC <- apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC", "QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,min)

  best_model <- c("random","ToM_BT","ToM_NBT", "ToM_NT","QL_states","S_EWA", "MBM")[apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)]
  # 
 exp2_model_comp <- rbind(exp2_model_comp ,
                       data.frame(
                         "human_id" = id,
                         "condition" = dat_exp2[dat_exp2$human_id==id,"condition"][1],
                         "Early_game_score" = tr_score,
                         "Total_score" = tot_score,
                         "Best_model" = best_model,
                         "Total_time" = sum(tdat$human_rt),
                         "TR_minus_NT_BIC" = id_results[,"Btwn_TR_BIC"] - id_results[,"No_Btwn_Tr_BIC"],
                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC

@@

cor.test(exp2_model_comp$TR_minus_NT_BIC, exp2_model_comp$Early_game_score, method="spearman")

@@

exp2_model_comp$model <- recode(exp2_model_comp$Best_model,"Bayes Tr" = "Tranfer","Bayes NT" = "No Transfer", "QL_states" = "Q_Learning",  .default = "Random")
model <- factor(exp2_model_comp$model)
condition <- factor(exp2_model_comp$condition)

>>>>

# Assumes within game transfer of opponent model between stages, but boolena for between game transfer. 
# TOM_model <- function(par, data, opp_strategy_vec, return_value, within_transfer, btwn_transfer) {
#   
#   # dat = data subset for one participant
#   # opp_strategy_vec = vector of possible opponent strtegies, model assumes humans restrict opp strategy space to vector   c("level0","level1","level2")
#   # return = -2logLik 
#   # or "likelihood_by_trial" vector  (for later plotting, etc)
#   # btwn_transfer is a boolean. True if distribution of opponent strategies is kept across games. False otherwise. 
#   
#   # theta = parameter, probability computer will play its best response to what it thinks human is. Truth = 90%. in [0,1].
#   # eps: parameter controlling noise in human choice. Probability human will DEVIATE from its best response. In [0,1].
#   theta <- par[1]
#   eps <- par[2]
#   
#   num_strat = length(opp_strategy_vec) 
#   
#   # Load tables predicting oppponent movel
#   
#   rps_predict_opp <- read.csv("rps_predict_opp.csv")
#   fwg_predict_opp <- read.csv("fwg_predict_opp.csv")
#   shootout_predict_opp <- read.csv("shootout_predict_opp.csv")
#   
# 
#   #lik_opp is a vector that holds and updates probability distribution of opp strategy given actions.
#   lik_opp <- matrix(0.0,num_strat, nrow(data))
#   
#   # Initiate prior vectors for each opponent as uniform
#   opp_prior_vec <- rep(1/num_strat, num_strat)
#   opp1_prior_vec <-rep(1/num_strat, num_strat)
#   opp2_prior_vec <-rep(1/num_strat, num_strat)
#   
#   lik_hum <- matrix(0.0,nrow(data))
#   # br_hum is vector that stores best responses of human to actions taken by each level-k ai opponent at the round.
#   br_hum <- rep(NA,num_strat)
# 
#   
#   for(t in 1:nrow(data)) {
#     t_game <- data[t,"game"]
#     pred_file_opp <- switch(as.character(t_game),rps = rps_predict_opp,fwg = fwg_predict_opp, shootout = shootout_predict_opp)
#     nopts <- 3
#     if(data[t,"round"] == 1) {
#       # first round is uniform prediction
#       pred_opp <- NA
#       lik_hum[t] <- 1/nopts
#       
#       ## KEY CODE FOR LEARNING TRANSFER !! (if no OM transfer reset prior to uniform)#####
#       # Round 1 of stage 1 
#       if (data[t,"stage"] == 1) {
#         if (btwn_transfer){
#           # if there is between game transfer, then the opp_prior_vec should have stored what was learned about the SECOND opponent 
#           # ...from stage 4 of previous game (or uniform if it is first game of RPS). store that before proceeding
#           opp2_prior_vec <- opp_prior_vec
#           # if between game transfer use stored opp1 prior vector from previous game (or uniform if first game  RPS) 
#           opp_prior_vec <- opp1_prior_vec
# 
#         } else { # <- No between game TRANSFER 
#           opp_prior_vec <- rep(1/num_strat, num_strat)
#         }
#         
#       # we are round 1 of stage 2, keep opp vector from round 20 of stage 1  for stage 3
#         } else if (data[t,"stage"] == 2) {
#           if (within_transfer){
#             # hold the probs vector of Opp type learned in stage 1 in memory and save to temp.
#             opp1_prior_temp <- opp_prior_vec
#           if (btwn_transfer){
#             # If  between games transfer get prior from opp2 prior saved from last stage of last game 
#             opp_prior_vec <- opp2_prior_vec
#           } else { # if no between transfer start of first interaction with secnd opp should be reset
#             opp_prior_vec <- rep(1/num_strat, num_strat)
#           }
#           
#         } else { # Assume no between game transfer if no within. reasonable. 
#           opp_prior_vec <- rep(1/num_strat, num_strat)    
#         }
#         
#       # we are round 1 of stage 3
#       } else if (data[t,"stage"] == 3) {
#         if (within_transfer) {
#           # if within_transfer keep opp vector from round 20 of stage 2 for stage 4
#           opp2_prior_temp <- opp_prior_vec
#           # if within_transfer, use what we learned about opp1 in stage 1 as new prior.  
#           opp_prior_vec <- opp1_prior_temp
#           
#         } else { # No within transfer, dont store anything and reset priors
#           opp_prior_vec <- rep(1/num_strat, num_strat)    
#         }
# 
#       
#       # We are in round 1 of stage 4,
#       }  else if (data[t,"stage"] == 4) {
#         if (within_transfer) {
#           if (btwn_transfer) {
#             # Store what was learned about opponent 1 for nxt game...
#            opp1_prior_vec <- opp_prior_vec
#           } 
#           # Use what was learned about opponent 2 from stage 2.
#           opp_prior_vec <- opp2_prior_temp
#           
#         } else {
#           opp_prior_vec <- rep(1/num_strat, num_strat)
#         }
#         
#       }
#       
#     # Rounds 2 to End of stage
#     } else {
#       cat("stage", data[t,"stage"], " opps ",  opp_prior_vec, "\n")
#       # get prediction of opponent action from CSV files
#       for (strategy in opp_strategy_vec) {
#         k = match(strategy,opp_strategy_vec)
#         pred_opp <- as.character(filter(pred_file_opp, pred_file_opp$human_previous == as.character(data[t-1,"h_action"]) & pred_file_opp$computer_previous == as.character(data[t-1,"a_action"]))[[strategy]])
#         
#         # Given opponent action predicted, what would be human action best response for each opp strat
#         br_hum[[k]] <- exp2_best_response(t_game,as.character(pred_opp))
#         
#         # First we deal with easy case of unique predicted action ( multiple possible preds in shoot are separated by "/" sign)
#         if (!grepl("/",pred_opp,fixed = TRUE)) {
#            # Multiply prior by likelihood of observation to get posterior. Done here ot take advantage of For loop. 
#           if(as.character(data[t,"a_action"]) == pred_opp) {
#             lik_opp[k,t] <- (theta + (1-theta)/nopts)*opp_prior_vec[k]
#           } else {
#             lik_opp[k,t] <- ((1-theta)/nopts)*opp_prior_vec[k]
#           }
#         # Here we are in shootout and opponent predicted action is a vector of two possible moves (e.g "left/center")  
#         } else {
#           if(grepl(as.character(data[t,"a_action"]), pred_opp,fixed = TRUE)) {
#             # Assume each action has likelihood of 50%
#              lik_opp[k,t] <- 0.5*(theta + (1-theta)/nopts)*opp_prior_vec[k]
#           } else {
#             #the 2 is to standardise the theta dependent probs: P(ai plays pred | opp is level k)
#             lik_opp[k,t] <- 2*((1-theta)/nopts)*opp_prior_vec[k]
#           }
#         }
#         
#       # Get which opponent strategy human current actn maps to (i.e, if index = 0 then human current action is best response to level-0 comp_strat...)
#       indices <- which(grepl(as.character(data[t,"h_action"]),br_hum,fixed = TRUE))
# 
#       # THEN likelihood of current human action is just prior on opponent vec (haven't updated priors with curr opp act yet)
#       # if action is not predicted by any level-k OM, assume human chooses randomly with prob eps
#       if(length(indices) == 0){
#         lik_hum[t] <- eps/nopts
#       # if same br action for multiple possible ai opponents, add probabilities 
#       } else {
#         lik_hum[t] <- sum(opp_prior_vec[indices])*(1-eps) + eps/nopts
#       }
#     }  
#       # Standardising the probabilities and updating prior
#       lik_opp[,t] <- lik_opp[,t]/sum(lik_opp[,t])
#       opp_prior_vec <- lik_opp[,t]
#     }
#   # for debugging uncomment the line below
#   #cat(as.character(pred_opp),as.character(data[t,"a_action"]),lik_opp[,t],"/n")
#   }
#   
#   if(return_value == "-2loglik") {
#     ret <- -2*sum(log(lik_hum))
#     if(is.infinite(ret) || is.nan(ret)) {
#       return(1e+300)
#     } else {
#       return(ret)
#     }
#   }
#   if(return_value == "likelihood_by_trial") return(lik_hum)
#   
# }

```{r}
# Assumes within game transfer of opponent model between stages, but boolena for between game transfer. 
TOM_model <- function(par, data, opp_strategy_vec, return_value, within_transfer, btwn_transfer, Naive = FALSE) {

@@

      ## KEY CODE FOR LEARNING TRANSFER !! #####
      #Naive 
      if (Naive) {
        # pass. no update to prior vector throughout all rounds and games
      } else {
        #abc
        #def
        # Round 1 of stage 1 
        if (data[t,"stage"] == 1) {
          if (btwn_transfer){
            # if there is between game transfer, then the opp_prior_vec should have stored what was learned about the SECOND opponent 
            # ...from stage 4 of previous game (or uniform if it is first game of RPS). store that before proceeding
            opp2_prior_vec <- opp_prior_vec
            # if between game transfer use stored opp1 prior vector from previous game (or uniform if first game  RPS) 
            opp_prior_vec <- opp1_prior_vec
          } else { # <- No between game TRANSFER 
            opp_prior_vec <- rep(1/num_strat, num_strat)
          }

@@

      } #End of no naive condition

@@

TOM_model(c(0.8,0.1),test_data,c("level0","level1","level2"),"-2loglik", within_transfer = FALSE, btwn_transfer = FALSE, Naive = TRUE)
```
## Fitting Bayesian model with between game transfer (as well as within)  
```{r, cache=TRUE}
exp2_BT <- list()
for(id in unique(dat_exp2$human_id)) {
  exp2_BT[[id]] <- list()
  tdat <- subset(dat_exp2,human_id == id)

@@

  exp2_BT[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = TRUE, btwn_transfer = TRUE, Naive = FALSE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
}
save(exp2_BT, file="exp2_BT.RData")

@@

  exp2_NO_BT[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = TRUE, btwn_transfer = FALSE, Naive = FALSE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
}

@@

  exp2_NO_Tr[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = FALSE , btwn_transfer = FALSE, Naive =FALSE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
}

@@

#Fitting model where player does not distinguish between opponents 
```{r, cache=TRUE}

exp2_Naive <- list()
for(id in unique(dat_exp2$human_id)) {
  exp2_Naive[[id]] <- list()
  tdat <- subset(dat_exp2,human_id == id)

  # exp2_Naive[[id]] <- DEoptim(fn=naive_bayes, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))

  exp2_Naive[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = FALSE , btwn_transfer = FALSE, Naive = TRUE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
}

save(exp2_Naive,file="exp2_Naive.RData")
```

## Fitting Q_learning with state space of possible last round plays 
```{r, cache=TRUE}
exp2_QL_states <- function(par,data,return_value,gamma, within_transfer = FALSE){
  # Par[1] -> beta= inverse temperature parameter in softmax choice function
  # Par[2] -> lambda = learning rate (one per game?)
  # data : participant and ai choice data.
  # return_value=c("-2loglik","likelihood_by_trial")
  # Gamma is discount factor for future rewards 
  # Returns Q-values per trial and predicts choice using softmax
  beta <- par[1]
  alpha <- par[2]

@@

    if(data[t,"round"] == 1) {

      # Within game transfer Code 
      if (!within_transfer){
              Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, shootout = Q_vals_SHOOT)
      } else {
        if (data[t,"stage"] == 1){
          Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, shootout = Q_vals_SHOOT)
        } else if (data[t,"stage"] == 2) {
          Q_vals_opp1 <- Q_vals
          Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, shootout = Q_vals_SHOOT)
        } else if (data[t,"stage"] == 3) {
          Q_vals_opp2 <- Q_vals 
          Q_vals <- Q_vals_opp1
        } else if (data[t,"stage"] == 4) {
          Q_vals <- Q_vals_opp2
        }
      }

      #cat(Q_vals,"\n") 
      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, shootout = states_SHOOT)
      # first round is uniform prediction
      lik_hum[t] <- 1/nopts
      # Randomly select state and previous actions for first round
      curr_state <- sample(state_vec, size = 1)
      h_act <- sample(colnames(Q_vals), size =1)
      ai_act <- sample(colnames(Q_vals), size =1)
      reward <- 0

@@

    # Assume human chooses action probabilistically using softmax on Q values
    probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
    #if (data[t,"round"] == 1) { cat(probs,"\n") }

@@

```{r}
exp2_QL_states(c(5,0.4),test_data, "-2loglik", 0.0, TRUE)
```

@@

```{r, cache=TRUE}
exp2_QLS_within_Tr <- list()
for(id in unique(dat_exp2$human_id)) {
  exp2_QLS_within_Tr[[id]] <- list()
  tdat <- subset(dat_exp2,human_id == id)
  # QL_states_modelling[[id]] <- optim(c(1,0.1),fn=Q_learn_states,gr = NULL, data=tdat,"-2loglik", gamma =0 , lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")

   exp2_QLS_within_Tr[[id]] <- DEoptim(fn=exp2_QL_states,lower = c(0,0), upper = c(20,1), data=tdat,"-2loglik", gamma = 0, within_transfer =TRUE, control=list(trace = FALSE, parallelType=1))
}

save(exp2_QLS_within_Tr , file="exp2_QLS_within_Tr.RData")
```

##Self tuning EWA model

@@

@@

                         # Bayesian updating with/without transfer
                         "Btwn_TR_BIC" = exp2_BT[[id]]$value + 2*log(180),
                         "No_Btwn_Tr_BIC" = exp2_NO_BT[[id]]$value+ 2*log(180),
                         "No_Tr_BIC" = exp2_NO_Tr[[id]]$value+ 2*log(180),
                         "Naive_BIC" = exp2_Naive[[id]]$value+ 2*log(180),

                         # Theta is the parameter governing AI stochasticity. Truth is 0.9
                         "theta_transfer" = exp2_BT[[id]]$par[1],
                         "theta_no_btw_tr" = exp2_NO_BT[[id]]$par[1],
                         "theta_no_tr" =  exp2_NO_Tr[[id]]$par[1],
                         "theta_naive" = exp2_Naive[[id]]$par[1],
                         # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
                         "eps_transfer" = exp2_BT[[id]]$par[2],
                         "eps_no_btwn_tr" = exp2_NO_BT[[id]]$par[2],
                         "eps_no_tr" = exp2_NO_Tr[[id]]$par[2],
                         "eps_naive" = exp2_Naive[[id]]$par[2],

                         # Q-learning with last round states (No within transfer)
                         "QL_states_BIC" = exp2_QLS_modelling[[id]]$optim$bestval + 2*log(180),
                         # beta ->  inverse temperature parameter in softmax choice function
                         "QL_states_Beta" = exp2_QLS_modelling[[id]]$optim$bestmem[1],
                         # alpha -> learning rate in QL update
                         "QL_states_alpha" = exp2_QLS_modelling[[id]]$optim$bestmem[2],

                         # QLS assuming within game transfer
                         "QLS_within_Tr_BIC" = exp2_QLS_within_Tr[[id]]$optim$bestval + 2*log(180),
                         # beta ->  inverse temperature parameter in softmax choice function
                         "QLS_within_Tr_Beta" = exp2_QLS_within_Tr[[id]]$optim$bestmem[1],
                         # alpha -> learning rate in QL update
                         "QLS_within_Tr_alpha" = exp2_QLS_within_Tr[[id]]$optim$bestmem[2],

@@

```{r}
exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT","ToM_Naive", "QL_states","QLS_within","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])

@@

```{r}
exp2_model_comp <- data.frame()
for(id in unique(dat_exp2$human_id)) {
  tdat <- subset(dat_exp2,human_id == id)
  tot_score <- sum(tdat$score)
  tot_time <- sum(tdat$human_rt)
  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg"))
  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
  tr_score <- sum(early_dat$score)
  id_results <- subset(exp2_results, ID == id)
  min_BIC <- apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC", "QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,min)

  best_model <- c("random","ToM_BT","ToM_NBT", "ToM_NT","ToM_Naive","QL_states","QLS_within","S_EWA", "MBM")[apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)]
  # 
  exp2_model_comp <- rbind(exp2_model_comp ,
                       data.frame(
                         "human_id" = id,
                         "condition" = dat_exp2[dat_exp2$human_id==id,"condition"][1],
                         "Early_game_score" = tr_score,
                         "Total_score" = tot_score,
                         "Best_model_2" = best_model,
                         "Total_time" = sum(tdat$human_rt),
                         "BT_minus_NBT_BIC" = id_results[,"Btwn_TR_BIC"] - id_results[,"No_Btwn_Tr_BIC"],
                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC

@@

cor.test(exp2_model_comp$BT_minus_NBT_BIC, exp2_model_comp$Early_game_score, method="spearman")

@@

exp2_model_comp$model <- recode(exp2_model_comp$Best_model,"ToM_BT" = "btwn Tranfer","ToM_NBT" = "No btwn Transfer", "ToM_NT" = "No within or btwn Tr","QL_states" = "Q_Learning",  .default = "Random")
model <- factor(exp2_model_comp$model)
condition <- factor(exp2_model_comp$condition)
